Prediction of the 2020 Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd
bruh

```{r ageind, echo=FALSE, fig.cap="Distribution of Age in Nationscape data"}
individual_survey <- readRDS(here::here("inputs/cleaned_data","individual-survey.rds"))
post_strat <- readRDS(here::here("inputs/cleaned_data","post-strat.rds"))

@@

@@

```{r racedis, echo=FALSE, fig.cap= "Votes by Race in Nationscape data"}
#these graph were done as EDA to see if there were any notable trends
s <-cont %>% 
  select(vote_2016, race) %>% 
  group_by(race, vote_2016) %>% 
  summarise(n = n()) %>% 
  mutate(freq = n/sum(n))
## 2016 vote by race
s %>% ggplot(aes(x = vote_2016, fill = race, group = race)) + 
  geom_bar(aes(y = freq), stat = "identity", position = "dodge", alpha = 2/3) + 
  labs(x = "Race", title = " Percentage of 2016 Presidential Election Votes by Race")
```

@@

```{r, echo=FALSE}
# make predictions using our model with data from post-strat data set

@@

## comparison on age
```{r age, echo=FALSE, include=FALSE, fig.cap="Distribution of Age between ACS and Nationscape data"}
individual_age_dist<- individual_survey %>% 
  group_by(age) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "Nationscape")

@@

## comparison on sex

```{r}
individual_sex_dist<- individual_survey %>% 
  group_by(sex) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "Nationscape")

@@

```{r sex_vote,fig.cap="Which individual did the candidate vote for? 2020 on the left, 2016 on the right"}
#figure to see 2020 voting by sex
vote_2020_sex <- individual_survey %>% 
  mutate(vote_2020 = if_else(vote_2020 == 1,"Donald Trump","Joe Biden")) %>% 
  group_by(sex,vote_2020) %>% 
  tally() %>% 
  ggplot(aes(x=sex, y = n)) + 
  geom_col() + 
  facet_grid(~vote_2020)+ labs(x = "Sex", y = "Number of people")

@@

Figure (@fig) indicates that a man is much more likely to vote for Trump than a woman is. This trend is also observed in the 2016 elections when Hillary Clinton, a woman, ran for office.

```{r survey_election_results}
individual_survey %>% mutate(vote_2020 = if_else(vote_2020 == 1,"Donald Trump","Joe Biden")) %>% group_by(vote_2020) %>% tally() %>% rename(candidate = vote_2020, votes = n ) %>% knitr::kable(caption = "Polling results for 2020 Election")
```
The above table indicates that Trump is most likely to win. This is captured from Nationscape data.

@@

```{r, echo = FALSE}

>>>>

```{r ageind, echo=FALSE, fig.cap="Distribution of Age in Nationscape data", message = FALSE}
individual_survey <- readRDS(here::here("inputs/cleaned_data","individual-survey.rds"))
post_strat <- readRDS(here::here("inputs/cleaned_data","post-strat.rds"))

@@

s <-cont %>% 
  select(vote_2016, race) %>% 
  group_by(race, vote_2016) %>% 
  summarise(n = n()) %>% 
  mutate(freq = n/sum(n))
```

@@

```{r racedis, echo=FALSE, fig.cap= "Votes by Race in Nationscape data"}
#these graph were done as EDA to see if there were any notable trends

## 2016 vote by race
s %>% ggplot(aes(x = vote_2016, fill = race, group = race)) + 
  geom_bar(aes(y = freq), stat = "identity", position = "dodge", alpha = 2/3) + 
  labs(x = "Race", title = " Percentage of 2016 Presidential Election Votes by Race")
```

@@

```{r, echo=FALSE, include = FALSE}
# make predictions using our model with data from post-strat data set

@@

## Comparison on Age
```{r age, echo=FALSE, fig.cap="Distribution of Age between ACS and Nationscape data", message = FALSE}
individual_age_dist<- individual_survey %>% 
  group_by(age) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "Nationscape")

@@

## Comparison on Sex

```{r, echo = FALSE,  message = FALSE}
individual_sex_dist<- individual_survey %>% 
  group_by(sex) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "Nationscape")

@@

```{r sex_vote, fig.cap="Which individual did the candidate vote for? 2020 on the left, 2016 on the right", echo = FALSE, message = FALSE}
#figure to see 2020 voting by sex
vote_2020_sex <- individual_survey %>% 
  mutate(vote_2020 = if_else(vote_2020 == 1,"Donald Trump","Joe Biden")) %>% 
  group_by(sex,vote_2020) %>% 
  tally() %>% 
  ggplot(aes(x=sex, y = n)) + 
  geom_col() + 
  facet_grid(~vote_2020)+ labs(x = "Sex", y = "Number of people")

@@

(Figure \@ref(fig:sex_vote) indicates that a man is much more likely to vote for Trump than a woman is. This trend is also observed in the 2016 elections when Hillary Clinton, a woman, ran for office.

```{r survey_election_results, echo = FALSE}
individual_survey %>% mutate(vote_2020 = if_else(vote_2020 == 1,"Donald Trump","Joe Biden")) %>% group_by(vote_2020) %>% tally() %>% rename(candidate = vote_2020, votes = n ) %>% knitr::kable(caption = "Polling results for 2020 Election")
```
The above table indicates that Trump is most likely to win. This is captured from Nationscape data.

@@

```{r, echo = FALSE, message = FALSE}
